SRG operator evolution

### 2019-06-04 Notes/SRG_operator_evolution/srg_operator_evolution.tex
Added SRG-evolved potential figures to these SRG operator evolution notes.
Re-organized figures.
Now organizing figures by topic instead of date. For example, SRG operator evolution figures go to Figures/SRG_operator_evolution. LaTeX notes use these figures directly.
Added captions to SRG-evolved potential figures.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% File: srg_operator_evolution.tex
%
% Author: A. J. Tropiano (tropiano.4@osu.edu)
% Date: May 20, 2019
%
% Notes on SRG operator evolution project.
%
% Revision history:
% 	05/31/19 --- Renamed magnus.tex from magnus_Jan08.tex. - Renamed to srg_operator_evolution.tex from operator_evolution_May20.tex.
%			   Added a description of computing SRG unitary transformations. Added momentum projection operator contours and momentum %                         distribution plots.
%	06/03/19 --- Added brief descriptions of how to numerically compute momentum projection operators and distributions.                           
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}
\usepackage[font=small,skip=0pt]{caption} % For captions on figures and tables
\usepackage{cellspace}
\usepackage{color}
\usepackage{enumerate}
\usepackage{epsfig}
\usepackage[figuresright]{rotating}
\usepackage{float}
\usepackage{hyperref} % For clickable links to sections within table of contents
\usepackage{graphicx}
\graphicspath{{Figures/}} % Setting the graphics path
\usepackage{physics} % For bra-ket notation
\usepackage{siunitx}
\usepackage[caption=false]{subfig} % For sub-figures

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Block-diag3,00}%
	}
	\caption{Caption.}
	\label{potential_contours_kvnn10_3S1}
\end{figure}

@@

-- The top row of Fig.~\ref{momentum_projection_contours_q3,00_kvnn10} should match the top row in Fig. 4 of \cite{Anderson:2010aq}.
-- Smeared delta function comment.
-- Compared block-diagonal to Wegner.
-- Another note about block-diagonal.

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn106_3S1_Block-diag2,00}%
	}
	\caption{Caption.}
	\label{potential_contours_kvnn106_3S1}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn107_3S1_Block-diag2,00}%
	}
	\caption{Caption.}
	\label{potential_contours_kvnn111_3S1}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn111_3S1_Block-diag2,00}%
	}
	\caption{Caption.}
	\label{potential_contours_kvnn111_3S1}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn112_3S1_Block-diag2,00}%
	}
	\caption{Caption.}
	\label{potential_contours_kvnn112_3S1}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn222_3S1_Block-diag3,00}%
	}
	\caption{Caption.}
	\label{potential_contours_kvnn222_3S1}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn224_3S1_Block-diag2,00}%
	}
	\caption{Caption.}
	\label{potential_contours_kvnn224_3S1}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn222_3S1_Block-diag3,00}%
	}
	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Gezerlis et al. N$^2$LO local potential with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c). Here $q=3$ fm$^{-1}$ and the EFT cutoff is $1$ fm.}
	\label{momentum_projection_contours_q3,00_kvnn222}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn224_3S1_Block-diag2,00}%
	}
	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Gezerlis et al. N$^2$LO local potential with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b). Here $q=3$ fm$^{-1}$ and the EFT cutoff is $1.2$ fm.}
	\label{momentum_projection_contours_q3,00_kvnn224}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% File: srg_operator_evolution.tex
%
% Author: A. J. Tropiano (tropiano.4@osu.edu)
% Date: May 20, 2019
%
% Notes on SRG operator evolution project.
%
% Revision history:
% 	05/31/19 --- Renamed magnus.tex from magnus_Jan08.tex. - Renamed to srg_operator_evolution.tex from operator_evolution_May20.tex.
%			   Added a description of computing SRG unitary transformations. Added momentum projection operator contours and momentum
%                         distribution plots.
%	06/03/19 --- Added brief descriptions of how to numerically compute momentum projection operators and distributions. Also added SRG-
%        		   evolved potential contours for comparison with other operators.                  
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}
\usepackage[font=small,skip=0pt]{caption} % For captions on figures and tables
\usepackage{cellspace}
\usepackage{color}
\usepackage{enumerate}
\usepackage{epsfig}
\usepackage[figuresright]{rotating}
\usepackage{float}
\usepackage{hyperref} % For clickable links to sections within table of contents
\usepackage{graphicx}
\graphicspath{{../../Figures/SRG_operator_evolution/}} % Setting the graphics path
\usepackage{physics} % For bra-ket notation
\usepackage{siunitx}
\usepackage[caption=false]{subfig} % For sub-figures

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn10_3S1_Block-diag3,00}%
	}
	\caption{Matrix elements of the Entem-Machleidt N$^3$LO non-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).}
	\label{potential_contours_kvnn10_3S1}
\end{figure}

@@

-- The top row of Fig.~\ref{momentum_projection_contours_q3,00_kvnn10} should match the top row in Fig. 4 of \cite{Anderson:2010aq}.
\\
-- Smeared delta function comment.
\\
-- Compared block-diagonal to Wegner.
\\
-- Another note about block-diagonal.

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn106_3S1_Block-diag2,00}%
	}
	\caption{Matrix elements of the RKE N$^3$LO semi-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b). Here the EFT cutoff is $450$ MeV.}
	\label{potential_contours_kvnn106_3S1}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn107_3S1_Block-diag2,00}%
	}
	\caption{Matrix elements of the RKE N$^3$LO semi-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b). Here the EFT cutoff is $500$ MeV.}
	\label{potential_contours_kvnn111_3S1}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn111_3S1_Block-diag2,00}%
	}
	\caption{Matrix elements of the RKE N$^4$LO semi-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b). Here the EFT cutoff is $450$ MeV.}
	\label{potential_contours_kvnn111_3S1}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn112_3S1_Block-diag2,00}%
	}
	\caption{Matrix elements of the RKE N$^4$LO semi-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b). Here the EFT cutoff is $500$ MeV.}
	\label{potential_contours_kvnn112_3S1}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn222_3S1_Block-diag3,00}%
	}
	\caption{Matrix elements of the Gezerlis et al.~N$^2$LO local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c). Here the EFT cutoff is $1$ fm.}
	\label{potential_contours_kvnn222_3S1}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{potential_contours_kvnn224_3S1_Block-diag2,00}%
	}
	\caption{Matrix elements of the Gezerlis et al.~N$^2$LO local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b). Here the EFT cutoff is $1.2$ fm.}
	\label{potential_contours_kvnn224_3S1}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn222_3S1_Block-diag3,00}%
	}
	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Gezerlis et al.~N$^2$LO local potential with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c). Here $q=3$ fm$^{-1}$ and the EFT cutoff is $1$ fm.}
	\label{momentum_projection_contours_q3,00_kvnn222}
\end{figure}

@@

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{momentum_projection_contours_q3,00_kvnn224_3S1_Block-diag2,00}%
	}
	\caption{Matrix elements of $\mel{k}{a^{\dagger}_q a_q}{k'}$ SRG-evolving in $\lambda$ right to left under transformations from the Gezerlis et al.~N$^2$LO local potential with the Wegner generator (a) and block-diagonal generator decoupling at $\Lambda=2$ fm$^{-1}$ (b). Here $q=3$ fm$^{-1}$ and the EFT cutoff is $1.2$ fm.}
	\label{momentum_projection_contours_q3,00_kvnn224}
\end{figure}
